Notes

### 2022-06-09 Notes.Rmd
network viz updates (bipartite + one-mode)
updates and figures

>>>>

One could force it to be bipartite by changing name according to category. Once bipartite, use the one mode projections to calculate network statistics more relevant for influence. For example a weighted betweenness or something like that.

### EGRMs

- use constraints on degree: keep degrees constant. But not sure how to code it
- Play with control features:
        - MCMCLE.maxit = < 60 which is the current default (how do I get the defaults?)
